Untargeted control doc

### 2023-10-09 untargeted/paruntargeted_control.Rmd
Fixing some erroneous annotations

```{r rescue feats rendering, eval=FALSE}
anno_manu <- readxl::read_excel("untargeted/manual_annotations.xlsx") %>%
  filter(amendment==!!amendment)
all_feat_data <- read_csv(paste0(output_folder, "all_feat_data.csv"))
best_feat_data <- read_csv(paste0(output_folder, "best_feat_data.csv"))
anno_manu %>%
  filter(str_detect(notes, "[Rr]escue"))
all_feat_data %>%
  filter(mzmed%between%pmppm(128.0325, 10))
# 128.0325, 130.047052, 174.1365
mass_check(128.0325)
```

@@

>>>>

```{r rescue feats rendering, eval=FALSE}
anno_manu <- readxl::read_excel("untargeted/manual_annotations.xlsx") %>%
  filter(amendment==!!amendment)
all_feat_data <- read_csv(paste0(output_folder, "all_feat_data.csv"))
best_feat_data <- read_csv(paste0(output_folder, "best_feat_data.csv"))
anno_manu %>% filter(str_detect(notes, "[Rr]escue"))
all_feat_data %>% filter(mzmed%between%pmppm(128.0325, 10))
```

@@

anno_manu %>%
  select(compound_name, feature, mz) %>%
  filter(!feature=="NA") %>%
  left_join(all_feat_data) %>%
  ggplot(aes(label=feature)) +
  geom_point(aes(x=mz, y=mzmed-mz)) +
  geom_abline(slope = 1, intercept = 0)
